\chapter{Literature Review}

In an time of austerity and double dips in the economy, \gls{IB} is playing `the game' not only over products and customers but also with institutions. 
Companies like Apple and Samsung are  fighting in court over~\gls{IP} in a multitude of countries. 
The cell phone department of Motorola was bought by Google solely because of it's numerous \glspl{IP}. The field not limited to \glspl{IP}. 
Next to the fight over \gls{IP} subsidies are at the forefront of the public debate as well. 
Boeing and Airbus have been fighting over subsidies for decades where on more than one occasion the \gls{WTO} has ruled on the validity of these subsidies. 
More recently solar panels have become a topic of tariffs between the European Union and China. \\

The field of play is governed by governments, trade blocks and the \gls{WTO} on the one hand and \gls{IB} on the other.
A multitude of forces are acting on this playing field and the different actors on this pitch have to cooperate. 
Different \gls{MNE} will cope differently with the challenges that are set by the institutions and the environment that they are operating in. That this environment is of importance is explained by \gls{IBV}~\cite{Kostova:1999,Meyer:2009,Wang:2012} 

\section{History of Strategy in IB Literature}
Using the examples of Google, Apple, Samsung, Boeing and Airbus strategies of the large~\mne have extended. It is no longer just resources and industries that dictate the strategies that companies employ. 
According to~\cite{Peng:2009}, the market-based institutional framework has been taken for granted, and formal institutions (such as laws and regulations) and informal institutions (such as cultures and norms) have been assumed away as``background''.

This trent has given rise to what~\cite{Peng:2009} calls the `third leg' of the strategy tripod.~\Gls{IBV} has been an addition to the theories of~\gls{RBV} introduced by~\cite{Barney:1991} and industry based view by~\cite{Porter:1980}. 
Since being introduced by~\cite{Porter:1980} (Industry based view) and~\cite{Barney:1991} (~\gls{RBV}) strategic management (theory) or strategy in short, has gained a lot of momentum in the international business community. \\ 

\input{Porter}

\input{Barney}

Both theories of Porter and Barney made their respective impressions in Strategic literature.  However~\gls{RBV}, which in introspective in nature and \gls{InBV} is extrospective cannot account for the entire spectrum of conscious decision making.
Considering the theories of Barney and Porter the Dutch `Plofkip' \footnote{Loosley translated in English as BangChick} would be a highly successful product.\\
In the 2010s in the Netherlands a new breed in chicks (a broiler) was bread. From a scientific standpoint this was a very successful product with regard to sustainability and food conversion. 
This `plofkip' as it was rebranded by the media and animal welfare organisations has certain traits that are very positive\footnote{taken from websites (\url{http://fransvdst.wordpress.com/2012/10/28/het-duurzame-vleeskuiken})}\footnote{Dutch newspaper `Trouw'
(\url{http://www.trouw.nl/tr/nl/5948/Dierenwelzijn/article/detail/3267278/2012/06/07/De-voordelen-van-de-plofkip.dhtml}) 
and (\url{http://www.trouw.nl/tr/nl/4332/Groen/article/detail/3324936/2012/10/01/Vanuit-het-milieu-gezien-is-er-niets-mis-met-plofkip-en-megastal.dhtml})}
These broilers had noticeable advantages:

\begin{itemize}
 \setlength{\itemsep}{1pt}
\item The broiler grows faster than the free-range chicken carcass weight (40 days vs. 56 days) and need to be fed so less time and therefore needs to be less manure removed
 \item    The broiler grows better with less feed than the free-range chicken (has better feed conversion called). There is the free-range chicken so need more feed to grow. One kilogram of meat
\item     The broiler has less stable space at his disposal including what should be heated
\item     The manure of a broiler remains in the stable and is thus more environmentally friendly processes
  \item   The broiler is so tender and cook faster
\end{itemize}
Despite all these advantages, the disadvantages (cleverly supported by pictures) that the chickens had such difficulties as supporting their own bodyweight and their harts having issues coping with the high growth rate~\footnote{taken form \url{http://www.wakkerdier.nl/actueel/plofkip-campagne and translated freely by the author}}, the broiler had to be abandoned and is no longer `in play' as a food source.\\
The aforementioned example can not be explained by the theories by~\cite{Porter:1980,Barney:1991}, they cannot explain for this phenomenon. 
The lack of context in with this product has to `operate'  and the power of institutions are not catered for in the theories of Barney and Porter.

\input{Peng}

\input{Institution_Theory}
